\cvsection{Work Experience}

\begin{cventries}
  \vspace{-2mm}
  \cventry
    {Technical Lead, API Platform}
    {\href{https://www.kaluza.com/}{Kaluza}}
    {Lisbon, Portugal (Full Remote)}
    {Sep 2024 – Present}
    {
    \begin{cvitems}
      \item Designed KaPI's SLA Maturity model on query complexity, turning production data into SLAs and tightening governance across 400+ resolvers.
      \item Own external API gateways: GraphQL (scaled to \textbf{1k req/s} for the largest client) and Event Streaming (operations).
      \item Designed a global-first registration model for API composition and market/client isolation, cutting time to new markets.
      \item Reduced Datadog logging costs by \textbf{\textasciitilde{}\$240k/year} by making logs outcome-driven so cost per request stays predictable.
      \item Cut new-environment spin-up from \textbf{\textasciitilde{}2 weeks to 3 days}, shortening time-to-first-use for new clients.
      %\item Sped up the local development cycle and automated API registration into the documentation site, cutting manual cross-team setup.
    \end{cvitems}
    \vspace{4mm}
    \skilltaglist{Scala,Typelevel,GraphQL,Event Stream Processing,Kafka,AWS,Terraform,Kubernetes,Databricks}
  }
  \cventry
    {Backend Software Engineer, Data Platform}
    {}
    {}
    {Jun 2021 – Sep 2024}
    {
    \begin{cvitems}
      %\item Research \href{https://raw.githubusercontent.com/bphenriques/curriculum-vitae/master/content/mockup_kaluza_research.png}{self-serviceable access requests UX options} so that domain owners can track and manage permissions in Kaluza Data Mart.
      \item Led the design of a self-service access-request API, dropping turnaround from \textbf{5 minutes to 30 seconds}.
      \item Mentored and led upskilling of team members in functional Scala.
      %\item Designed and built a BigQuery library that bridges the Java SDK with the Typelevel stack to promote reusability and reliability.
      \item Designed, built, and launched a Kafka to BigQuery ingestion pipeline for Kaluza Data Mart (\textbf{15k events/sec}).
      %\item Developed example Scala projects and automated Scala Steward onboarding as part of the Scala caretaker community.
      \item Co-led a cross-team initiative to standardize external interface registration and governance (GraphQL, Events, Analytics).
      %\item Designed and built a GDPR Right To Erasure tool to manage PII information in BigQuery.
      \item Chose DynamoDB over PostgreSQL for the access pattern, cutting re-ingestion from \textbf{2 weeks to 30 minutes}.  % Daily Costs: ~7$* to around ~0.12$
    \end{cvitems}
    \vspace{4mm}
    \skilltaglist{Scala,Typelevel,Event Stream Processing,Kafka,AWS,GCP,Terraform,BigQuery,PostgreSQL,DynamoDB,Kubernetes}
  }
  % Other notes: Reduced Costs from 7$ a day to 0.12$ a day by moving from RDS to dynamo
  % Re-ingestion of topics from 2 weeks to ~30 minutes

  \vspace{0.25mm}

  \cventry
    {Backend Software Engineer}
    {\href{https://www.talkdesk.com/}{Talkdesk}}
    {Lisbon, Portugal}
    {May 2019 – May 2021}
    {
      \begin{cvitems}
        % https://talkdesk.com/cloud-contact-center/customer-engagement/outbound-dialer/
        \item Designed, built, and launched Outbound Dialer (\textbf{60k phone calls per day}).
        \item \textbf{Doubled} the Dialer Engine's call throughput by optimizing I/O in the critical path.
        \item Built a Phone Call Automation Framework to simulate real-world interactions and automate E2E tests.
        % \item Halved deployment time and improved its safety by automating the process and promoting explicit rollback procedures.
        %\item Mentored and took the lead on upskilling team members by conducting Spring Boot workshops.
      \end{cvitems}
      \vspace{4mm}
      \skilltaglist{Kotlin,Spring Boot,Redis,RabbitMQ,PostgreSQL,Docker,Kubernetes,Prometheus,Grafana,Telnyx,Twilio}
    }

  \vspace{0.25mm}
    
  \cventry
    {Backend Software Engineer (Feedzai Insights, multi-tenant Elastic Stack)}
    {\href{https://feedzai.com/}{Feedzai}}
    {Lisbon, Portugal}
    {Jul 2017 – May 2019}
    {
      \begin{cvitems}
        \item Designed, built, and launched Feedzai's Insights, a multi-tenant Elastic Stack solution for reporting and near real-time dashboards.
        \item Designed data ingestion pipelines for real-time events (from RabbitMQ) and historical data (from PostgreSQL).
      \end{cvitems}
      \vspace{4mm}
      \skilltaglist{Java,Scala,Elastic Stack,RabbitMQ,PostgreSQL,Docker,AWS,Event Stream Processing,Ansible,\href{https://vega.github.io/vega/}{Vega},\href{https://www.tableau.com/}{Tableau},Jenkins}
    }

  \vspace{0.25mm}

  \cventryShort
    {iOS Developer}
    {\href{https://www.carbonbybold.com/pt-pt/}{Carbon By Bold}}
    {Lisbon, Portugal}
    {Dec 2016 – Jul 2017}
%    {\skilltaglist{iOS,Swift,Realm,Objective-C,Core Location,RxSwift,SignalR}}
% Developed and launch 3 iOS applications.

  \vspace{0.25mm}

  \cventryShort
    {GSoC iOS Student (\href{https://docs.google.com/presentation/d/1yv4XuNNpTgDkyOjL9SSjGe7PSZuwpbah42mQCACxdXQ/}{2015}) \& GSoC iOS Mentor (\href{https://summerofcode.withgoogle.com/archive/2016/projects/5509901874888704/}{2016}/\href{https://summerofcode.withgoogle.com/archive/2017/projects/5508656065937408/}{2017})}
    {Google Summer of Code (GSoC) participant with \href{http://anitaborg.org/}{AnitaB.org} (Open Source)}
    {Lisbon, Portugal (Full Remote)}
    {GSoC 2015, 2016, and 2017}

  \vspace{0.25mm}

  \cventryShort
    {iOS Developer (\href{https://apps.apple.com/us/app/tecnico-lisboa/id959976468}{Técnico Lisboa iOS App})}
    {\href{http://fenixedu.org/}{FenixEdu}}
    {Lisbon, Portugal}
    {Oct 2014 – Nov 2015}
%    {\skilltaglist{iOS,Swift,Core Data,Realm,EventKit}}    
\end{cventries}
